---
title: "design_doc"
format: html
editor: visual
---

# Introduction

Building retrofit has gained lots of traction in recent years due to its potential to increase building energy performance, provide cost savings, and lower environmental emissions. While the design of new, efficient buildings is also a research area of interest, these projects require immense amounts of resources and energy. Retrofit measures provide an effective, sustainable solution to increase building energy performance while avoiding issues related to land-use and deforestation. Facades are a key focus in retrofit designs as they are the facilitator between the indoor and outdoor worlds. Passive-design strategies, in particular, provide easy to implement and simple interventions that can have a large impact on the building's total energy consumption. This report aims to investigate the interactions and effectiveness of three different facade retrofit measures including design, engineering, and nature based solutions.

-   Discuss specifics about Singapore so audience knows where this research is focused on

    -   Cooling dominated society

-   More about why facades are such a key research area, what is so interesting about them in terms of saving energy?

-   I want to use the phrase "built environment" somewhere bc I think it sounds really good

-   Mention the structure of the report, what the reader will find in each section etc.

# Background

-   Discuss the UCDL paper

-   Discuss BEM using EnergyPlus

-   Discuss some papers that looked at facade retrofit optimizations

-   What is the novelty of this work: looking at three different design approaches and doing a comparative analysis

# Methods

-   Study area and target building - explain why (similar to UCDL paper)

    -   Why choose only the central building - what is the significance

-   Energy simulation in energyplus

    -   I think I can leave out all the details about the previous model since that is all available in the other paper and I can just mention that all the settings are the same

        -   Benchmarking case?

    -   Weather data, using their developed one that proved to be the "best"

-   Intervention measures

    -   Numbers and justification with sources

    -   Discuss why these in particular were chosen, why do a three way study?

-   KPIs and output variables of interest

    -   Cooling demand of whole building
        -   **Zone Ideal Loads Supply Air Total Cooling Energy** is the district cooling energy consumed by the ideal loads system “cooling coil” to cool and dehumidify the supply air.
    -   Energy use intensity
    -   How cool the building is / how well it blocks solar heat
        -   **Surface Outside Face Incident Solar Radiation Rate per Area:** what's hitting each surface
        -   **Surface Outside Face Absorbed Shortwave Radiation Rate per Area:** how much is being absorbed
        -   **Surface Outside Face Temperature:** Skin temp
        -   **Surface Inside Face Temperature**
        -   **Surface Inside Face Conduction Heat Gain Rate:** Direct conductive gains from opaque envelope into zones

## Design Intervention

### Fixed Exterior Shading

E+ objects (Thermal Zones and Surfaces)

-   Shading:Overhang

-   Shading:Overhang:Projection (best for parametric analysis)

-   Shading:Fin

-   Shading:Fin:Projection

What to vary

-   Overhang depth: 0 (none) / 0.8 / 1.5 (deep) m

    -   Find source to backup numbers

-   Fin depth and spacing (optional second step)

Best facades to shade for highest payoff

-   west

-   south

## Engineering Intervention

### Cool coating (exterior walls)

Since the exterior walls were already created and already had a filed for the solar absorptance, I did not need to make any adjustments using the IDFeditor and I was able to immediately begin a parametric analysis using the param() function of eplusr. I first ran a test case to ensure that everything was working properly.

E+ objects (surface construction elements)

-   Material

-   Material:NoMass

What to vary

-   Solar absorptance: 0.7 (dark) / 0.4 (med) / 0.2 (cool)

## Nature Intervention

### Green roof

I added the Material:RoofVegetation class manually in the IDFEditor to have a baseline case for the parametric study. All the fields for the baseline case were filled in by default values as outlined in the InputOuput Reference manual. I also manually added a new construction object for the green roof, which has all the same elements as the original roof, but now includes the roof vegetation as the outermost layer.

E+ objects (surface construction elements)

-   Material:RoofVegetation

What to vary

-   Leaf area index: 0 (none) / 2.5 / 5 (lush)

-   Soil/ substrate thickeness

```{r}
library(gt)

#Assign values to variables
shading <- c(0.1, 0.5, 1)
absorptance <- c(0.7, 0.4, 0.2)
lai <- c(1, 2.5, 5)
assign <- c("Baseline", "Medium", "High")

#Create dataframe
df <- data.frame(
  "Scenario" = assign,
  "Overhang Depth" = shading,
  "Solar Absorptance" = absorptance,
  "Leaf Area Index" = lai,
  check.names = FALSE
)

#Create table
df |> 
  gt() |> 
  tab_header(title = "Values for Building Retrofit") |> 
  fmt_number(columns = 2:4, decimals = 2) |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  )

```

```{r}

```

# Results

Key performance indicators to focus on:

-   Annual cooling demand (ideal loads) (minimize)

-   Zone Operative Temperature

    -   overheating degree hours (minimize)

-   Whole building electricity

# Conclusion
