---
title: "design_doc"
format: html
editor: visual
---

## Design Intervention

### Fixed Exterior Shading

E+ objects (Thermal Zones and Surfaces)

-   Shading:Overhang

-   Shading:Overhang:Projection (best for parametric analysis)

-   Shading:Fin

-   Shading:Fin:Projection

What to vary

-   Overhang depth: 0 (none) / 0.8 / 1.5 (deep) m

    -   Find source to backup numbers

-   Fin depth and spacing (optional second step)

Best facades to shade for highest payoff

-   west

-   south

## Engineering Intervention

### Cool coating (exterior walls)

E+ objects (surface construction elements)

-   Material

-   Material:NoMass

What to vary

-   Solar absorptance: 0.7 (dark) / 0.4 (med) / 0.2 (cool)

## Nature Intervention

### Green roof

E+ objects (surface construction elements)

-   Material:RoofVegetation

What to vary

-   Leaf area index: 0 (none) / 2.5 / 5 (lush)

-   Soil/ substrate thickeness

```{r}
library(gt)

#Assign values to variables
shading <- c(0, 0.8, 1.5)
absorptance <- c(0.7, 0.4, 0.2)
lai <- c(0, 2.5, 5)
assign <- c("Baseline", "Medium", "High")

#Create dataframe
df <- data.frame(
  "Scenario" = assign,
  "Overhang Depth" = shading,
  "Solar Absorptance" = absorptance,
  "Leaf Area Index" = lai,
  check.names = FALSE
)

#Create table
df |> 
  gt() |> 
  tab_header(title = "Building Retrofit Scenarios") |> 
  fmt_number(columns = 2:4, decimals = 2) |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  )

```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
